Spin canonical rings of log stacky curves

### 2015-07-07 curves-write-up/spin_cring.tex
added new example

Next, we construct the canonical ring of $R_L$ from $R_{L_X}$. By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1.$ We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
\begin{align*}
	R_L \cong k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))
\end{align*}
Indeed, such a relation must exist, because by Riemann--Roch, $h^0(\sx,4L)$

>>>>

Next, we construct the canonical ring of $R_L$ from $R_{L_X}$. By Riemann Roch, we see there is some element $y_{1,3} \in (R_L)_3$ with $\ord_{P_1}(y_{1,3}) = -1.$ We claim that there exist $a_1, a_2 \in k$ and a degree 4 polynomial $f(x_1, x_2) \in k[x_1,x_2]$ such that
\begin{align*}
	R_L \cong k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))
\end{align*}
First, note that $x_1,x_2,y_{1,3}$ generate all of $R_L$ from the Generalized Max Noether Theorem for genus 0 curves, as described in Voight
and Zureick-Brown \cite[Lemma 3.1.1]{vzb:stacky}. That is, the maps
\begin{align*}
	H^0(\sx,L) \otimes H^0(\sx,nL) \rightarrow H^0(\sx, (n+1)L)
\end{align*}
are surjective. Next, note that a relation of the form $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ must exist, because by Riemann--Roch, $h^0(\sx,4L ) - h^0(\sx,4L_X) = 1,$ but $x_1 y_{1,3},x_2 y_{1,3}$ define two linearly independent elements of $h^0(\sx,4L ) \setminus h^0(\sx,4L_X).$ To complete the example, it suffices to show there are no additional relations. First, note that $a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)$ is necessarily irreducible because there are no relations among $x_1, x_2$ and $y_{1,3}$ in lower degrees. Hence, it follows that $k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2)) \rightarrow R_L$ is a surjection. Furthermore,
$\proj k[x_1,x_2,y_{1,3}]/(a_1 x_1 y_{1,3} +a_2 x_2 y_{1,3} + f(x_1,x_2))$ is 1 dimensional and integral, while $\proj R_L$ is also 1 dimensional. Therefore, the surjection must be an isomorphism, as claimed.
